IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-02 review/response_2.tex

\newenvironment{point}
	{\refstepcounter{point} \bigskip \noindent {\textbf{Comment~\thepoint} } ---\ \itshape}
	{\par}

\newenvironment{response}
	{\refstepcounter{response} \medskip \noindent \textbf{Response:}\ }
	{\medskip}

\begin{document}
	\includepdf{letter_2.pdf}

	\begin{editor}
		\begin{point}
			Please double-check Proposition~\ref{M-pr:bcd} and the algorithm may not converge to a local optimal due to the coupling constraint~\eqref{M-co:original_rate}.
		\end{point}

		\begin{response}
			Thank you for pointing this out. The editor is referred to Response~\ref{re:3.1}.
		\end{response}

		\begin{point}
			Please discuss the convergence criteria in details and justify the formulated optimization problem.
		\end{point}

		\begin{response}
			Please refer to Response~\ref{re:1.4}.
		\end{response}

		\begin{point}
			How does the IRS passive beamforming impact on the waveform design compared with existing systems?
		\end{point}

		\begin{response}
			Please refer to Response~\ref{re:2.2}.
		\end{response}

		\begin{response}
			Please refer to Response~\ref{re:2.3}.
		\end{response}
	\end{editor}

@@

			For GP Algorithm~\ref{M-al:gp}, the computational complexity is exponential w.r.t. the number of subbands \cite{M-Chiang2005}.
			\begin{framed}
				The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{M-al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{M-Chiang2005}.
			\end{framed}

			For M-SCA Algorithm~\ref{M-al:m_sca}, each optimization problem involved is an SDP with $(L+1)$ variables and linear constraints, and the computational complexity is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$ where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations.
			\begin{framed}
				Compared with Algorithm~\ref{M-al:sca}, the rate constraint \eqref{M-co:irs_rate} is dropped and each SDP in Algorithm~\ref{M-al:m_sca} involves $(L+1)$ linear constraints. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{M-Luo2010}. Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point since the current expression is dropped and no SCA is involved.
			\end{framed}

			For BCD Algorithm~\ref{M-al:bcd}, since Algorithm~\ref{M-al:gp} is involved per iteration, the computational complexity is exponential w.r.t. the number of subbands.
			\begin{framed}
				The steps are summarized in the BCD Algorithm~\ref{M-al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{M-al:gp}.
			\end{framed}

			For LC-BCD Algorithm~\ref{M-al:lc_bcd}, both waveform and active beamforming are obtained in closed form, and the computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
			\begin{framed}
				Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
			\end{framed}

			% As for the measurements, we evaluate the converging speed of all proposed algorithms. Figs.~\ref{fi:convergence_sca}--\ref{fi:convergence_bcd} show the output DC current versus the number of iterations for one channel realization at the WPT point. It is observed that the SCA- and BCD-based algorithms typically converge within \num{3} iterations while the GP-based algorithm takes around \num{9} iterations to converge. Those figures are not added to the manuscript due to the space constraint.
			% \begin{figure}[!t]
			% 	\centering
			% 	\subfloat[SCA-based\label{fi:convergence_sca}]{
			% 		\resizebox{0.32\columnwidth}{!}{
			% 			\input{../assets/convergence_sca.tex}
			% 		}
			% 	}
			% 	\subfloat[GP-based\label{fi:convergence_gp}]{
			% 		\resizebox{0.32\columnwidth}{!}{
			% 			\input{../assets/convergence_gp.tex}
			% 		}
			% 	}
			% 	\subfloat[BCD-based\label{fi:convergence_bcd}]{
			% 		\resizebox{0.32\columnwidth}{!}{
			% 			\input{../assets/convergence_bcd.tex}
			% 		}
			% 	}
			% 	\caption{Converging trend of the proposed algorithms for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$..}
			% \end{figure}
			\label{re:1.1}
		\end{response}

@@

		\begin{point}
			Since this paper focused on IRS-aided SWIPT systems, it could be better if the authors can further enrich the survey part to make the paper more comprehensive. In particular, some papers have considered this kind of problem from a different aspect such as \cite{Xu2021}. It is kindly suggested to briefly discuss the main difference between \cite{Xu2021} and the problem considered in this paper.
		\end{point}

		\begin{response}
			Thank you for sharing this paper. Instead of optimizing the phase shift of each IRS element, it tailored a tile-based two-stage optimization framework for large-scale IRS to enable a flexible performance-complexity tradeoff. The model also adapts well to practical IRS models accounting AoA and AoD. In contrast, our paper is more focused on waveform design and rate-energy tradeoff for one SWIPT user with practical co-located information decoder and energy harvester. We have updated the manuscript as follows.
			\begin{framed}
				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity. It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.

				\textellipsis To the best of our knowledge, all existing IRS-aided SWIPT papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
			\end{framed}
		\end{response}

@@

	\begin{reviewer}
		\begin{point}
			Although this paper reveals many useful insights, most of them are obtained via simulation and then explained via text. The overall theoretical contributions can be greatly improved if the authors can analytically verify or prove some of them, especially those unique to this paper. The authors may conduct the analysis under some simplified or special cases. If some of the observations and findings have been verified in existing papers, the authors can cite and echo these papers wherever necessary.
		\end{point}

		\begin{response}
			We believe the reviewer was referring to the array gain and scaling law suggested by Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}. Recall that $M$ refers to the number of transmit antenna, $N$ refers to the number of subbands, and $L$ refers to the number of IRS elements. From the perspective of WIT, coherent transmission achieves an array gain of $M$ \cite{M-Tse2005} and coherent reflection achieves an array gain of $L^2$ \cite{M-Wu2019}. From the perspective of WPT, \cite{M-Clerckx2016a} and \cite{M-Clerckx2018b} analytically proved the scaling law of the modulated and multisine waveforms. Even if a suboptimal waveform scheme (uniform power allocation in the frequency domain and matched filter in the spatial domain) is used, when $M$ is sufficiently large, the expectation of the DC current scales quadratically with $M$. We have cited those papers in the revised manuscript.

			Next, we verify the last observation where the expectation of the DC current scales quartically with $L$ in a much simplified scenario. Consider a SISO WPT system in a frequency-flat channel. We assume a sufficiently large $L$ such that the auxiliary link is dominant and the contribution of direct channel is omitted. With uniform power allocation to multisine ($s_{\mathrm{P},n} = \sqrt{2P}/\sqrt{N}$) in the frequency domain, the DC current writes as
			\begin{equation}
				z_{\mathrm{UP}} = \beta_2 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^2 P + \frac{3}{8} \beta_4 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^4 F,
			\end{equation}
			where $\beta_2$ and $\beta_4$ are fixed rectenna parameters, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$ are the path loss of incident and reflected links, $X$ is the random variable that models the small-scale double fading through one IRS element at any subband, and
			\begin{equation}
				F = \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} s_{n_1} s_{n_2} s_{n_3} s_{n_4} = \frac{4(2N^2+1)}{3N} P^2.
			\end{equation}
			Taking expectation over $\lvert X \rvert$, we have
			\begin{equation}
				\bar{z}_{\mathrm{UP}} = \beta_2 \Lambda_{\mathrm{I}}^2 \Lambda_{\mathrm{R}}^2 L^2 \mathbb{E}\{\lvert X \rvert^2\} P + \frac{3}{8} \beta_4 \Lambda_{\mathrm{I}}^4 \Lambda_{\mathrm{R}}^4 L^4 \mathbb{E}\{\lvert X \rvert^4\} \frac{2N^2+1}{2N} P^2,
			\end{equation}
			which verifies the scaling order of $L^4$. The analysis is not presented in the manuscript due to the space constraint.
		\end{response}

@@

		\begin{point}
			The authors are suggested to study the impact of IRS passive beamforming on the waveform design without IRS. For example, they can show the optimized waveforms with versus without IRS to unveil the interplay between them. Or even better, analytically compare the two waveforms.
		\end{point}

		\begin{response}
			Thank you for the suggestion. Too see this, we first show two realizations of direct channel amplitude (without IRS) and composite channel amplitude (with IRS) for WIT and WPT in Fig.~\ref{fi:channel_amplitude}. It is observed that under the configuration of choice, the WPT-optimized passive beamforming tends to concentrate the channel energy to relatively strong subbands, while the WIT-optimized passive beamforming achieves some balance among all subbands (similar to water-filling at high SNR).

			\begin{figure}[!h]
				\centering
				\resizebox{0.6\columnwidth}{!}{
					\includegraphics{../assets/channel_amplitude_100reflectors}
				}
				\caption{Channel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
				\label{fi:channel_amplitude}
			\end{figure}

			On the other hand, the corresponding amplitude of modulated and multisine waveforms are shown in Fig.~\ref{fi:waveform_amplitude}. Note that no multisine is used for WIT and the case is not shown. It is observed that although passive beamforming can enable a flexible resource allocation opportunity at the channel (please refer to Response~\ref{re:2.10} for details), its impact on waveform design is unobvious.

			\begin{figure}[!h]
				\centering
				\subfloat[WIT waveform: modulated]{
				\resizebox{0.32\columnwidth}{!}{
						\input{../assets/waveform_wit_modulated_100reflectors.tex}
					}
				}
				\subfloat[WPT waveform: modulated]{
					\resizebox{0.32\columnwidth}{!}{
						\input{../assets/waveform_wpt_modulated_100reflectors.tex}
					}
				}
				\subfloat[WPT waveform: multisine]{
					\resizebox{0.32\columnwidth}{!}{
						\input{../assets/waveform_wpt_multisine_100reflectors.tex}
					}
				}
				\caption{Sorted modulated and multisine amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
				\label{fi:waveform_amplitude}
			\end{figure}
			\label{re:2.2}
		\end{response}

@@

		\begin{point}
			In the introduction, it is suggested to also discuss the new design challenges posed by the nonlinear model compared to the existing designs under the linear model.
		\end{point}

		\begin{response}
			We believe this is an important issue and have modified the manuscript accordingly as follows.
			\begin{framed}
				\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model proposed in \cite{M-Clerckx2016a}. Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency compensation (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and non-concavity from high-order objective function.
			\end{framed}
			\label{re:2.3}
		\end{response}

@@

		\begin{point}
			In the low-complexity BCD, it is unclear how the authors dealt with the optimization of $\rho$ and $\delta$. In Algorithm~\ref{M-al:lc_bcd}, both of them are input. Did the authors perform a two-dimensional search here? Besides, they were assumed to be identical in the simulation. How will this assumption influence the performance loss?
		\end{point}

		\begin{response}
			Thank you for raising this point. The combining ratio $\delta$ determines the weight on multisine power waveform at the transmitter, while the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver. We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point. Heuristically, $\delta$ and $\rho$ should approximately equal at each point to boost R-E tradeoff. Indeed, the LC-BCD algorithm intends to draw the R-E tradeoff by performing a two-dimensional search that adjusts $\delta$ and $\rho$ from \num{1} to \num{0}. However, based on the deduction above, we set $\delta=\rho$ is the simulation and obtain the R-E region by one-dimensional search instead. The results show that even a one-dimensional search for the LC-BCD algorithm can achieve a very good performance. We have summarized the point in the manuscript as follows.
			\begin{framed}
				\textellipsis where the combining ratio $\delta$ determines the weight on multisine power waveform at the transmitter and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver\footnotemark.

				\textellipsis the LC-BCD algorithm draws the R-E tradeoff by performing a two-dimensional search that adjusts $\delta$ and $\rho$ from \num{1} to \num{0}.

@@

				\textellipsis assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).

				\textellipsis \emph{Third,} the LC-BCD algorithm achieves a very good R-E performance even if one-dimensional search is considered for $\delta=\rho$ over $[0,1]$. This conclusion is also verified in the following plots.
			\end{framed}
			\footnotetext{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point. Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost R-E tradeoff.}
		\end{response}

		\begin{point}
			If possible, in Figs.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz}, the authors can show the performance of the design under the conventional linear harvester model, so as to show how much performance loss it would incur.
		\end{point}

		\begin{response}
			We would like to clarify that the performance loss under the conventional linear harvester model is revealed instead in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}. Figs.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz} are intended to compare different IRS strategies when both waveform and passive beamforming are designed under nonlinear harvester model. The authors believe that to design passive beamforming under linear harvester model when the waveform is designed under nonlinear harvester model might confuse the readers. On the other hand, we agree with the reviewer that the performance loss under linear harvester deserves more attention, and have changed the label in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector} from `ASS' to `LEH' and revised the manuscript as follows to make this point clear.
			\begin{framed}
				\emph{Second,} the conventional Linear Energy Harvester (LEH) model leads to power-inefficient design. To show the underlying performance loss, we truncate the DC objective function \eqref{M-eq:z} at $n_0=2$ such that, 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required, 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{M-Clerckx2016a}. As shown in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} current gap compared to the nonlinear model-based SMF and GP.
			\end{framed}
		\end{response}

### 2021-08-03 assets/waveform_wit_modulated.tex
:bento: Update assets

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,3.312in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

@@

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,2.598in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.16127375477314\\
2	3.16328124696217\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	3.16000164000459\\
2	3.16455204336543\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.883in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=4.47213595499958,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	2.23287518822941\\
2	2.2349269985345\\
3	2.23712082213722\\
4	2.2393436833526\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.23243942623434\\
2	2.23535811809091\\
3	2.23559687073864\\
4	2.24086923394096\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.56947570711734\\
2	1.57851757716824\\
3	1.58044033841813\\
4	1.58155392693919\\
5	1.58198101788601\\
6	1.58501068613205\\
7	1.5854415059255\\
8	1.58662414938375\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.56539227519679\\
2	1.57784161002588\\
3	1.57927371173129\\
4	1.58176667731984\\
5	1.58367655185228\\
6	1.58456745246925\\
7	1.58798555735369\\
8	1.58848608357287\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,0.454in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.10024627987476\\
2	1.10664679147412\\
3	1.11204358490005\\
4	1.11548794498246\\
5	1.11636022580843\\
6	1.11667878555116\\
7	1.11706894724375\\
8	1.11773783143934\\
9	1.11958645829829\\
10	1.12088764958973\\
11	1.1221919201651\\
12	1.12315337822569\\
13	1.12435794296855\\
14	1.12469670812645\\
15	1.12549793104218\\
16	1.12556826383419\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.09504669861652\\
2	1.10317579191466\\
3	1.11227601228037\\
4	1.11361418816502\\
5	1.11483774301138\\
6	1.11656722620907\\
7	1.11743910790233\\
8	1.11769734992669\\
9	1.11854798737502\\
10	1.12003038718696\\
11	1.12377646668063\\
12	1.12467567262626\\
13	1.12655148101693\\
14	1.1274126433068\\
15	1.12796634097065\\
16	1.12836437582839\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,3.296in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,2.586in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=3.16339693422903,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.16197544010622\\
2	3.16257985135002\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	3.16115798980538\\
2	3.16339693422903\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,1.877in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=2.24021589430493,
ytick={0, 2, 4},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	2.23378952118842\\
2	2.23654464483002\\
3	2.23679993610816\\
4	2.23713622127432\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.22545319620151\\
2	2.23919103086275\\
3	2.23937811584463\\
4	2.24021589430493\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=2,
ytick={0, 1, 2},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.57492536161738\\
2	1.58019558798915\\
3	1.58142030797172\\
4	1.58199169722726\\
5	1.58244513043393\\
6	1.58255247448636\\
7	1.58277901011216\\
8	1.58278544606781\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.54658301793324\\
2	1.57890604600973\\
3	1.58567053153604\\
4	1.58602764687811\\
5	1.58742152113889\\
6	1.58776504632019\\
7	1.58809335949322\\
8	1.5881928373826\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=2,
ytick={0, 1, 2},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.10693759886133\\
2	1.11152957304454\\
3	1.1153740214668\\
4	1.11770662066146\\
5	1.11834620668734\\
6	1.11879936603067\\
7	1.11890444505621\\
8	1.11953756000214\\
9	1.11961027059849\\
10	1.1199195311366\\
11	1.12011494881618\\
12	1.12017416958603\\
13	1.12033284686217\\
14	1.12033895948864\\
15	1.12040846172897\\
16	1.12041390652564\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.05608889731275\\
2	1.08431501210806\\
3	1.10834050856176\\
4	1.11891055117252\\
5	1.12321530567299\\
6	1.12470216682288\\
7	1.12523793678797\\
8	1.12552298915589\\
9	1.12642268676024\\
10	1.12689100352585\\
11	1.127202079253\\
12	1.12763006638833\\
13	1.12766695997673\\
14	1.12788476342969\\
15	1.1278991085713\\
16	1.12794901573584\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%
